GlobalSearchRegression.jl: \\ Building bridges between Machine Learning and Econometrics in Fat-Data scenarios

### 2019-10-01 paper/paper.tex
Update paper.tex

The aim of this paper is twofold. The first one is to describe a novel research-project aimed at building bridges between machine learning and econometric worlds. The second one is to introduce the main characteristics and comparative performance of the first Julia-native all-subset regression algorithm included in \verb GlobalSearchRegression.jl  (v1.0.3). As other available alternatives, this algorithm allows researchers to obtain the best model specification among all possible covariate combinations - in terms of user defined information criteria-, but up to 3165 and 197 times faster than STATA and R alternatives, respectively.

@@

In table 1, we present a performance comparison of our GLobalSearchRegression Julia-package against its main alternatives: MuMin-pdredge and GSREG (written in R and Stata\footnote{The parallel version of Stata-GSREG is still under development. A preliminary version is available upon request from authors}, respectively).
Execution times were obtained from a HED architecture using a Threadripper 1950x build, with 16 cores (32 threads) overclocked to 3.8GHz and 64 GiB of DDR4-RAM at 3200Mhz. Comparative scripts were implemented on Julia 1.0.3, R 3.6.0 and Stata 15 IC, running on Ubuntu 18.04.2 LTS -Linux kernel 4.15-\footnote{All these test are available \href{https://github.com/ParallelGSReg/GlobalSearchRegression.jl/tree/master/juliacon2019proceedings/reproducibility}{here}} \vskip 6pt

>>>>

The aim of this paper is twofold. The first one is to describe a novel research-project designed for building bridges between machine learning and econometric worlds. The second one is to introduce the main characteristics and comparative performance of the first Julia-native all-subset regression algorithm included in \verb GlobalSearchRegression.jl  (v1.0.3). As other available alternatives, this algorithm allows researchers to obtain the best model specification among all possible covariate combinations - in terms of user defined information criteria-, but up to 3165 and 197 times faster than STATA and R alternatives, respectively.

@@

In table 1, we present a performance comparison of our GLobalSearchRegression Julia-package against its main alternatives: MuMin-pdredge and GSREG (written in R and Stata\footnote{The parallel version of Stata-GSREG is still under development. A preliminary version is available upon request from authors}, respectively).
Execution times were obtained from a HED architecture using a Threadripper 1950x build, with 16 cores (32 threads) overclocked to 3.8GHz and 64 GiB of DDR4-RAM at 3200Mhz. Comparative scripts were implemented on Julia 1.0.3, R 3.6.0 and Stata 15 IC, running on Ubuntu 18.04.2 LTS -Linux kernel 4.15-\footnote{All these test are available \href{https://github.com/ParallelGSReg/GlobalSearchRegression.jl/tree/master/Reproducibility}{here}} \vskip 6pt
